Consumption and resistance across states and HRRs

### 2017-03-01 states/resistance/state-report.Rmd
improving state report

```{r setup}
library(broom)
library(pander)

@@

# Antibiogram data, with individual records
abg = read_tsv('../../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by='zipcode') %>%
  right_join(resistance_groups, by='drug') %>%
  filter(bug %in% organisms) %>%
  select(bug, drug_group, state, hrr, percent_nonsusceptible)

# Keep only those bug/drug combinations that are in at least 20 states
abg %<>%
  select(bug, drug_group, state) %>%
  distinct %>%
  count(bug, drug_group) %>%
  filter(n >= 20) %>%
  left_join(abg, by=c('bug', 'drug_group'))

@@

@@

```{r}
all_result %>%
  filter(place=='state') %>% 
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug, 
         explanatory, correlation, p.value,
         adj.p.value, sig) %>%
  kable
```

@@

```{r}
all_result %>%
  filter(place=='hrr') %>% 
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, consumption_drug, 
         explanatory, correlation, p.value,
         adj.p.value, sig) %>%
  kable
```

>>>>

```{r setup}
library(broom)
library(pander)
library(assertr)

@@

# Antibiogram data, with individual records
abg = read_tsv('../../../../antibiogram/data/abg.tsv', col_types=cols(zipcode='c')) %>%
  mutate(drug=tolower(drug), percent_nonsusceptible=100-percent_susceptible) %>%
  left_join(hrr, by='zipcode') %>%
  right_join(resistance_groups, by='drug') %>%
  filter(bug %in% organisms) %>%
  select(bug, drug_group, state, hrr, percent_nonsusceptible, n_isolates)

# Keep only those bug/drug combinations that are in at least 20 states
abg %<>%
  select(bug, drug_group, state) %>%
  distinct %>%
  count(bug, drug_group) %>% rename(n_states=n) %>%
  filter(n_states >= 20) %>%
  left_join(abg, by=c('bug', 'drug_group'))

@@

Linear models:

```{r}
safe_lm = function(data, indep, expl) {
  try(return(lm(sprintf('%s ~ %s', indep, expl), data) %>% tidy), silent=TRUE)
  data_frame(term=expl, estimate=NA, std.error=NA, statistic=NA, p.value=1.0)
}

linear_models = function(df, indep) {
  lapply(c('cpkp', 'did'), function(expl) {
    safe_lm(df, indep, expl) %>%
      filter(term==expl) %>%
      rename(explanatory=term) %>%
      verify(nrow(.) == 1)
  }) %>% bind_rows
}

linear_models_result = function(x, this_place) {
  x %>%
    group_by_('bug', 'drug_group', this_place) %>%
    summarize(mean_nonsus=mean(percent_nonsusceptible, na.rm=TRUE),
              cpkp=head(cpkp, 1),
              did=head(did, 1)) %>%
    group_by(bug, drug_group) %>%
    do(linear_models(., 'mean_nonsus')) %>%
    ungroup %>%
    filter(!is.na(estimate)) %>%
    mutate(adj.p.value=p.adjust(p.value, method='BH'),
           sig=pvalue_stars(adj.p.value)) %>%
    select(bug, drug_group,
           explanatory, slope=estimate, p.value,
           adj.p.value, sig)
}

linear_state_res = linear_models_result(state_dat, 'state')

linear_state_res %>% kable
```

end linear models

@@

```{r}
all_result %>%
  filter(place=='state') %>% 
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, drug_group, 
         explanatory, correlation, p.value,
         adj.p.value, sig) %>%
  kable
```

@@

```{r}
all_result %>%
  filter(place=='hrr') %>% 
  mutate_if(is.numeric, function(x) signif(x, digits=3)) %>%
  select(bug, drug_group, 
         explanatory, correlation, p.value,
         adj.p.value, sig) %>%
  kable
```
